Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-08-20 stp/paper_aaai/main.tex
Backing up everything, results section

In our case, we would like this global model to account not only for structural properties of the original data sources, but also to include the semantics, which is usually implicitly present in the sources.
In other words, we want to build a semantic model which describes the data sources in terms of concepts and relationships defined by an ontology \cite{Taheriyan2013}.
Henceforth, we focus on a specific data integration problem: automatically mapping a new relational data source onto a user provided ontology.

@@

In this paper we use Machine Learning techniques (ML) to learn mapping rules from already mapped instances.
To this end we formulate the Relational-To-Ontology Mapping Problem (\relonto{}) as a Minimum Cost Steiner Tree Problem (STP) with side constraints \cite{deuna2016steiner}.

Firstly, we build an \emph{integration graph} which includes the 
attributes from the new source as well as ontology classes and properties. 
Secondly, we apply machine learning techniques to 
assign costs to its edges. 
Lastly, we use Constraint Programming (CP) to 
find a minimum cost Steiner Tree in the graph.
The goal is to assign the costs on the edges in such a way that the resulting Steiner Tree is a valid semantic model for the new source.

The contributions of this work are:
\begin{itemize}
	\item \ddg{TODO}
\end{itemize}

@@

The first step to model the semantics of a new source $s^\star$ is to recognize the semantic types present in the source. 
We call this step \emph{semantic labeling}, which assigns a confidence value to a match of an attribute from $s^\star$ to a type $l \in 
\mathcal{L_O}$.
%\ddg{CHECK!}

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $S_T$ provide us the training sample.
We compute a feature vector for each source \ddg{Which features?} attribute and associate the known semantic type with the corresponding feature vector. We train a random forest on this sample. 
Then we use the learnt model to classify attributes in the new
source.

@@

The algorithm we used to construct $\mathcal{G_O}$ is the same as \cite{taheriyan2016learning} and is described in detail in their work.
Briefly, the algorithm has three parts:
\begin{enumerate}
\item Adding the known semantic models.
\item Adding the semantic types learned for the target source. \ddg{TODO: see 
Important note above}
\item Expanding the graph using the domain ontology $\mathcal{O}$.
\end{enumerate}

Note how the alignment graph contains data nodes that correspond to at least 
some of the semantic types. 
For instance, it could contain two nodes $City.name$ and $State.name$ rather than just one node $name$ connected to two 
nodes $City$ and $State$. 
We say these nodes are \emph{induced} into the 
alignment graph by the semantic types, we note them $\mathcal{D_{G_O}}$ and we 
call them \emph{data nodes} of the alignment graph.

@@

As an extension to the problem, we consider using pattern mining techniques in order to identify patterns in the training set of semantic model that repeat themselves often. 
The hope is that with such information we can encourage the semantic model $m^\star$ for the new source to use groups of edges that                                       appeared often together in training semantic models.

\npr{reformulate for typed directed multigraphs and example based on Fig3}
In our context, we define a \emph{pattern} is a graph $P$ that is undirected 
and simple (no multiple edges between two nodes, nor self-loops).

Let $G = (V_G,E_G,\lambda_G)$ and $P = (V_P,E_P, \lambda_P)$ be two graphs 
where $\lambda_G$ (resp. $\lambda_P$) is a \emph{labeling function} that maps 
nodes/edges of $G$ (resp. $P$) into a set of labels (e.g. natural numbers).
An \emph{embedding} of $P$ into $G$ is an injective function $f : V_G \mapsto 
V_P$ such that for all $x,y \in V_P$:
\begin{enumerate}
	\item $\{x,y\} \in E_P \implies \{f(x),f{y}\} \in E_G$.
	\item $\lambda_P(x) = \lambda_G(f(x))$
	\item $\lambda_P(\{x,y\}) = \lambda_G(\{f(x),f(y)\})$
\end{enumerate} 
That is, if an edge exists in $P$, it must also exist in $G$ (but not 
vice-versa); and the labelling functions of both graphs must match after 
applying the embedding function.

Our goal is to take a set of graphs (the semantic models from the training set 
$S_T$) and find patterns that appear often across that set of graphs. 
This is 
known as the Frequent Graph Pattern Mining, which contains the subgraph 
isomorphism, known to be NP-complete. 
There exists a range of tools that can achieve this task using Transactional 
Frequent Graph Pattern Mining~\cite{yan2002gspan}. 
We chose to use DIMSpan \cite{petermann2017dimspan}. 
\ddg{CHECK! How do they solve an NP-complete problem??}
\npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}

We obtain patterns of size upto 6 in under 4 minutes for the biggest instances in our evaluation framework. \npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe cite my work on how databases perform for graph pattern matching. Should it be better in related work?}

This tool provides us with a list of patterns that are frequent, as well as 
their support. 
The \emph{support} of a pattern is an anti-monotonous measure of frequency. 
Thus, the higher the support, the more often the pattern appears. This typically means that big patterns have low support.

@@

% baseline for evaluation
We choose \emph{Karma}~\cite{taheriyan2016learning} as our baseline.
This system also phrases the \relonto{} problem as STP and decomposes it further into two parts.
However, they use approximation algorithms both for the matching and for the STP parts.
Additionally, they do not consider unmatched attributes in the sources.
To ensure that Karma also handles such attributes, we change its semantic labeling model SemanticTyper~\cite{Ramnandan:Assigning} to ours and we add a special \emph{unknown} ontology which gives specification for \emph{root} and \emph{unknown} nodes of the alignment graph.
The first modification also ensures the fairness of evaluation since both Karma and Serene will have the same matches for attributes.

@@

% architecture
We have run all our experiments on a Dell server with 252 GiB of memory, 2 CPUs with 4 cores each, 1 Titan GPU and 1 GeForce 1080 Ti GPU.
\npr{check characteristics, AWS machine is bigger}

@@

We have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
Tab.~\ref{tab:semlab} provides evidence that our new semantic labeling model is better suited for the task when there are unmatched attributes in domains.
\npr{Explain}

@@

%%%
% performance figures
%%%
We evaluate our new system \emph{serene} and its modification \emph{serene-pats}, which uses graph patterns, against the state-of-the-art system \emph{karma}.
Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} show their performance on the museum and soccer domains.
We report average precision, recall and run times for the systems with regard to variable number of semantic models in the training set.

%%% museum domain
\begin{figure*}[ht]\small
\pgfplotsset{
    small,
    %legend style={legend pos=north east}
    legend style={
        at={(0.01,0.01)},
        anchor=south west,
    },
   }%
\begin{minipage}[b]{.34\linewidth}
\centering
\begin{tikzpicture}[baseline]
\begin{axis}[
		    xlabel={\emph{known semantic models}},
		    ylabel={Performance},
		    xmin=1, xmax=28,
		    ymin=0.2, ymax=0.9,
		    xtick={1,5,10,15,20,25,28},
		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
		    legend pos=south east,
		    ymajorgrids=true,
		    grid style=dashed
		]

@@

%%
As mentioned previously, the chuffed solver outputs solutions as it finds them.
In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we report the first found solutions.
In Fig.~\ref{fig:perfsol} we show how the performance of \emph{serene} changes across sequentially found solutions.
In all our experiments we use a timeout threshold of 15s for the chuffed solver.
Additionally, we investigate how the performance is influenced if we introduce a weighting scheme on the patterns,
i.e., costs of patterns are scaled by a factor. 
%% sequentially found solutions and different weights for patterns
\begin{figure*}[ht]\small
\pgfplotsset{
    small,
    %legend style={legend pos=north east}
    legend style={
        at={(0.01,0.01)},
        anchor=south west,
    },
   }%
\begin{minipage}[b]{.34\linewidth}
\centering
\begin{tikzpicture}[baseline]
\begin{axis}[
		    xlabel={\emph{solution}},
		    ylabel={Performance},
		    xmin=0, xmax=20,
		    ymin=0.7, ymax=1,
		    xtick={0,5,10,15,20},
		    ytick={0.7,0.8,0.9,1},
		    legend pos=south east,
		    ymajorgrids=true,
		    grid style=dashed,
		    legend style={at={(1.5,1.1)},anchor=south, legend columns=-1}
		]

@@

% change in performance if we look at sequentially found solutions
% only leave-one-out for museum domain with 15s timeout for chuffed
\begin{figure}\small
\begin{tikzpicture}\small
\pgfplotsset{
    scale only axis,
    small,
    xmin=0, xmax=9
}

@@

\begin{axis}[
  axis y line*=right,
  axis x line=none,
  ymin=0, ymax=15,
  legend pos=south east,
  ylabel=time (s)
]
\addlegendimage{/pgfplots/refstyle=plot_one}\addlegendentry{precision}
\addlegendimage{/pgfplots/refstyle=plot_two}\addlegendentry{recall}
\addplot[smooth,mark=square,blue]
  coordinates{
    (0,0.894338290115883)(1,2.39426428574782)(2,6.89703391393025)(3,10.3563708686829)(4,9.87668780326843)(5,9.92719115257263)(6,10.4045292949677)(7,14.3818371582031)(8,14.4026180458069)(9,14.8023208427429)
}; \addlegendentry{time}
\end{axis}
\end{tikzpicture}
\caption{Performance of chuffed for museum leave-one-out}\label{fig:loo}
\end{figure}

@@

As mentioned above, the approaches for mapping Web tables also perform semantic labeling.
They design various similarity metrics for attribute names and attribute values.
However, they disregard the attributes which are not matched to the ontology (the so-called \emph{unknown} class of attributes).
It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
That is why we have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.

>>>>

In our case, we would like this global model to account not only for structural properties of the original data sources, but also to include the semantics, which is usually implicitly present in the sources.
In other words, we want to build a semantic model which describes the data sources in terms of concepts and relationships defined by an ontology \cite{taheriyan2016learning}.
Henceforth, we focus on a specific data integration problem: automatically mapping a new relational data source onto a user provided ontology.

@@

In this paper we use Machine Learning techniques (ML) to learn mapping rules from previously mapped instances.
To this end we formulate the Relational-To-Ontology Mapping Problem (\relonto{}) as a Minimum Cost Steiner Tree Problem (STP) with side constraints \cite{deuna2016steiner}.

Firstly, we build an \emph{integration graph} which includes the 
attributes from the new source as well as ontology classes and properties. 
Secondly, we apply machine learning techniques to 
assign costs to its edges. 
Lastly, we use Constraint Programming (CP) to 
find a minimum cost Steiner Tree in the graph.
The goal is to assign the costs on the edges in such a way that the resulting Steiner Tree is a valid and coherent semantic model for the new source.

The contributions of this work are:\ddg{TODO}
\begin{itemize}
	\item A novel modeling framework for \relonto{} problem which seemlessly incorporates machine learning and constraint programming.
	\item An efficient approach to handle attributes which cannot be matched to the ontology. \npr{semantic labeling model and root, unknown nodes in the alignment graph and additional constraints} 
\end{itemize}

@@

The first step to model the semantics of a new source $s^\star$ is to recognize the semantic types present in the source. 
We call this step \emph{semantic labeling}, which assigns a confidence value to a match of an attribute from $s^\star$ to a type $l \in 
\mathcal{L_O}$.
Typically semantic labeling techniques encounter several problems.
Firstly, there can be naming conflicts~\cite{Pinkel:rodi}, including those cases where users represent the same data in different ways.
Secondly, semantically different attributes might have syntactically similar content, for example, startDate versus endDate for the Event class.
Thirdly, a considerable number of attributes which do not have any corresponding property in the ontology, either by accident or on purpose.
%\ddg{CHECK!}

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $S_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source \ddg{Which features?} and associate the known semantic type with the corresponding feature vector.
The feature vector includes characteristics of the attribute such as a number of whitespaces and other special characters, statistics of values in the column (e.g, mean/ max/ min string length and numeric statistics) and many more.
One of the important features characterising information content of an attribute is Shannon's entropy of the attribute's concatenated rows.
Shannon's entropy (or information entropy~\cite{Manning:Introduction}) of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary of all possible characters.
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The vocabulary of all characters consists of 100 printable characters (including $\backslash$n).
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
We also compute a set of features based on similarity metrics inspired by state-of-the-art works~\cite{Pham:semantic} or~\cite{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

The algorithm for the construction of the alignment graph $\mathcal{G_O}$ follows the ideas of~\cite{taheriyan2016learning}.
Briefly, the algorithm has three parts:
\begin{enumerate}
\item Adding the known semantic models.
\item Adding the semantic types learned for the target source. \ddg{TODO: see 
Important note above}
\item Expanding the graph using the domain ontology $\mathcal{O}$.
\end{enumerate}

Note how the alignment graph contains data nodes that correspond to at least 
some of the semantic types. 
For instance, it could contain two nodes $City.name$ and $State.name$ rather than just one node $name$ connected to two 
nodes $City$ and $State$. 
We say these nodes are \emph{induced} into the 
alignment graph by the semantic types.
We denote them as $\mathcal{D_{G_O}}$ and call them the \emph{data nodes} of the alignment graph.

@@

Certain patterns of connections can be prevalent in the domain.
For example, in Fig.~\ref{FIG:sem} both semantic models have class nodes ``City'', ``Organization'' and ``Person''.
According to the ontology in Fig.~\ref{FIG:onto} there are multiple ways to connect these nodes.
However, if we know that the ``Person'' works for the ``Organization'', then based on the known semantic models ``City'' is more likely to be the birth place of the ``Person'' rather than the location of the ``Organization''.
To increase the coherence of the generated semantic models, we would like to discover such patterns of connections.

%As an extension to the problem, we consider using pattern mining techniques in order to identify patterns in the training set of semantic model that repeat themselves often. 
%The hope is that with such information we can encourage the semantic model $m^\star$ for the new source to use groups of edges that                                       appeared often together in training semantic models.

\npr{reformulate for typed directed multigraphs and example based on Fig3}
In our context, patterns are typed directed graphs.
We mine these patterns from the set of semantic models in the training set $S_T$.
This is known as Transactional Frequent Graph Pattern Mining, which contains the subgraph 
isomorphism, known to be NP-complete.
The frequency of a pattern is an anti-monotonous measure, meaning that bigger patterns will have lower supports than their subgraphs.
We solve this pattern mining task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs and uses Apache Flink for scalability.  
We obtain patterns of size upto 6 in under 4 minutes for the biggest instances in our evaluation framework. 
\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe cite my work on how databases perform for graph pattern matching. Should it be better in related work?}

%Let $G = (V_G,E_G,\lambda_G)$ and $P = (V_P,E_P, \lambda_P)$ be two graphs 
%where $\lambda_G$ (resp. $\lambda_P$) is a \emph{labeling function} that maps 
%nodes/edges of $G$ (resp. $P$) into a set of labels (e.g. natural numbers).
%An \emph{embedding} of $P$ into $G$ is an injective function $f : V_G \mapsto 
%V_P$ such that for all $x,y \in V_P$:
%\begin{enumerate}
%	\item $\{x,y\} \in E_P \implies \{f(x),f{y}\} \in E_G$.
%	\item $\lambda_P(x) = \lambda_G(f(x))$
%	\item $\lambda_P(\{x,y\}) = \lambda_G(\{f(x),f(y)\})$
%\end{enumerate} 
%That is, if an edge exists in $P$, it must also exist in $G$ (but not 
%vice-versa); and the labelling functions of both graphs must match after 
%applying the embedding function.

%Our goal is to take a set of graphs (the semantic models from the training set 
%$S_T$) and find patterns that appear often across that set of graphs. 
%This is 
%known as the Frequent Graph Pattern Mining, which contains the subgraph 
%isomorphism, known to be NP-complete.  
%We solve this task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs and uses Apache Flink for scalability. 
%\ddg{CHECK! How do they solve an NP-complete problem??}
%\npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}
% 
%This tool provides us with a list of patterns that are frequent, as well as 
%their support. 
%The \emph{support} of a pattern is an anti-monotonous measure of frequency. 
%Thus, the higher the support, the more often the pattern appears. 
%This typically means that big patterns have low support.

@@

% baseline for evaluation
We choose \emph{Karma}~\cite{taheriyan2016learning} as our baseline.
This system also phrases the \relonto{} problem as STP and decomposes it further into two parts.
However, they use heuristic algorithms both for the matching and for the STP parts.
They solve the problems sequentially, i.e., once they produce a set of candidate mappings for attributes into the ontology, they fix this set and move onto the STP part.
Additionally, they do not consider unmatched attributes in the sources.
To ensure that Karma also handles such attributes, we change its semantic labeling model SemanticTyper~\cite{Ramnandan:Assigning} to ours and we add a special \emph{unknown} ontology which gives specification for \emph{root} and \emph{unknown} nodes of the alignment graph.
The first modification also ensures the fairness of evaluation since both Karma and Serene will have the same matches for attributes.

@@

% architecture
We have run all our experiments on a Dell server with 252 GiB of memory, 2 CPUs with 4 cores each, 1 Titan GPU and 1 GeForce 1080 Ti GPU.
\npr{check characteristics, AWS machine is bigger}
In all our experiments we use a timeout threshold of 15s for the chuffed solver.

@@

To evaluate our new system \emph{serene}, we show that its semantic labeling model produces more accurate matches for attributes and the CP formulation leads to better semantic models in terms of precision and recall.

We have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
Tab.~\ref{tab:semlab} provides evidence that our new semantic labeling model is better suited for the task when there are unmatched attributes in domains.
DSL uses heuristic measures to capture the similarity of attributes within the same class.
It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
Our intution why our approach performs better is that we have encorporated features which are derived directly from attribute values and are not based on the notion of similarity.
\npr{Good enough explanation?}

@@

%%%
% performance figures
%%%
%%% museum domain
\begin{figure*}[ht]\small
\pgfplotsset{
    small,
    %legend style={legend pos=north east}
    legend style={
        at={(0.01,0.01)},
        anchor=south west,
    },
   }%
\begin{minipage}[b]{.34\linewidth}
\centering
\begin{tikzpicture}[baseline]
\begin{axis}[
		    xlabel={\emph{known semantic models}},
		    ylabel={Performance},
		    xmin=1, xmax=28,
		    ymin=0.2, ymax=0.9,
		    xtick={1,5,10,15,20,25,28},
		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
		    legend pos=south east,
		    ymajorgrids=true,
		    grid style=dashed
		]

@@

% karma vs serene vs serene-pats
We evaluate our new system \emph{serene} and its modification \emph{serene-pats}, which uses graph patterns, against the state-of-the-art system \emph{karma}.
All three systems have access to the same set of matches produced by our semantic labeling model.
Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} show their performance on the museum and soccer domains.
We report average precision, recall and run times for the systems with regard to variable number of semantic models in the training set.
For \emph{serene} and \emph{serene-pats} we report the first solutions found by the chuffed solver.
We use default parameters for \emph{karma} which were shown to yield the best results~\cite{taheriyan2016learning}.
As we can see, \emph{serene} produces on average the best semantic models in terms of precision while \emph{serene-pats} generates slightly better models in terms of recall.
If we consider results separately per each instance and not on average, there are a few instances where \emph{karma} generates more precise models, however, our new approaches produce much better models in terms of recall in all considered instances. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% sequentially found solutions and different weights for patterns
\begin{figure*}[h]\small
\pgfplotsset{
    small,
    %legend style={legend pos=north east}
    legend style={
        at={(0.01,0.01)},
        anchor=south west,
    },
   }%
\begin{minipage}[b]{.34\linewidth}
\centering
\begin{tikzpicture}[baseline]
\begin{axis}[
		    xlabel={\emph{solution}},
		    ylabel={Performance},
		    xmin=0, xmax=20,
		    ymin=0.7, ymax=1,
		    xtick={0,5,10,15,20},
		    ytick={0.7,0.8,0.9,1},
		    legend pos=south east,
		    ymajorgrids=true,
		    grid style=dashed,
		    legend style={at={(1.5,1.1)},anchor=south, legend columns=-1}
		]

@@

%% sequential solution
As mentioned previously, the chuffed solver outputs solutions as it finds them.
In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we report the first found solutions.
In Fig.~\ref{fig:perfsol} we show how the performance of \emph{serene} changes across sequentially found solutions.
The idea is that the chuffed solver finds better solutions in terms of cost function, however, as we can see from the results,
that does not translate directly into more precise semantic models.
Additionally, we investigate how the performance is influenced if we introduce a weighting scheme on the patterns,
i.e., costs of patterns are scaled by a factor.
In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we use a scaling factor 1 for pattern costs.
Fig.~\ref{fig:perfsol} demonstrates that by using scaling factors 5, 10 or 20 for patterns from the museum domain we can generate semantic models which are almost 90\% in precision and recall.
This is a 20\% improvement in presision compared to the first solution found by \emph{serene-pats} and a 10\% improvement both in precision and recall for the first solution from \emph{serene}.
However, such improvement comes at a cost in run time.
On average, we have observed that the chuffed solver yields very good results already with the first found solution.
The sequential solutions are not always better, and hitting the optimal solution may take hours.

% change in performance if we look at sequentially found solutions
% only leave-one-out for museum domain with 15s timeout for chuffed
\npr{not sure whether Fig.~\ref{fig:loo} is needed}
\begin{figure}\small
\begin{tikzpicture}\small
\pgfplotsset{
    scale only axis,
    small,
    xmin=0, xmax=9
}

@@

\begin{axis}[
  axis y line*=right,
  axis x line=none,
  ymin=0, ymax=15,
  legend pos=south east,
  ylabel=time (s)
]
\addlegendimage{/pgfplots/refstyle=plot_one}\addlegendentry{precision}
\addlegendimage{/pgfplots/refstyle=plot_two}\addlegendentry{recall}
\addplot[smooth,mark=square,blue]
  coordinates{
    (0,0.894338290115883)(1,2.39426428574782)(2,6.89703391393025)(3,10.3563708686829)(4,9.87668780326843)(5,9.92719115257263)(6,10.4045292949677)(7,14.3818371582031)(8,14.4026180458069)(9,14.8023208427429)
}; \addlegendentry{time}
\end{axis}
\end{tikzpicture}
\caption{Performance of \emph{serene} for leave-one-out strategy on the museum domain.}\label{fig:loo}
\end{figure}

\npr{Maybe some words on how optimal solution found by chuffed relates to the ground truth?}

@@

As mentioned above, the approaches for mapping Web tables also perform semantic labeling.
They design various similarity metrics for attribute names and values.
However, they disregard the attributes which are not matched to the ontology (the so-called \emph{unknown} set of attributes) which are especially abundant on the Web~\cite{Ritze:matching}\cite{Pham:semantic}.
It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
That is why we have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
